### 2017-10-17 paper/sections/6_results.tex
paper: re-org eval and intro
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

We evaluate CudeleFS on a 15 node cluster, partitioned into 8 object storage
servers, 3 metadata servers, and 2 monitor servers. The object storage servers
double as clients which is fine because clients are CPU and memory bound while
object storage servers are disk IO bound. All daemons run as a single process
which is the default setting for Ceph and the nodes have 2 dual core 2GHz
processors with 8GB of RAM. There are three daemons per object storage server
(one for each disk formatted with XFS) and they share an SSD for the journal.
The nodes are running Ubuntu 12.04.4, kernel version 3.2.0-63 but all
experiments run in Docker containers; this makes it easier to tear down and
re-initialize the cluster ({\it e.g.}, dropping the kernel cache) between
experiments.

@@

\subsection{CudeleFS Mechanism Performance}

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-mechanisms.png}
\caption{
[\href{https://...}{source}]
The performance of the CudeleFS mechanisms normalized to the runtime of the
``Append Client Journal" mechanism (the runtime of writing \(n\) file creates
to the client's in-memory journal).  \label{fig:slowdown-mechanisms}}
\end{figure}

@@

Figure~\ref{fig:slowdown-mechanisms} shows the runtime of the CudeleFS
mechanisms, normalized to the time it takes to write \(n\) file create updates
to the client's in-memory journal ({\it i.e.} the ``Append Client Journal"
mechanism). Bars above \(10^0\) are slower than the ``Append Client Journal"
mechanism.  ``Stream" is an approximation of the
overhead and is calculated by subtracting the runtime of the job with the
journal turned off from the runtime with the journal turned on.  The largest
workload we tested is 100K file creates in the same directory.  This is the
maximum recommended size of a directory in CephFS; preliminary experiments with
larger directory sizes show memory problems.

\subsubsection{Poorly Scaling Data Structures} Despite doing the same amount of
work, mechanisms that rely on poorly scaling data structures have large
slowdowns for the larger number of creates. For example, ``RPCs" which relies
on the internal CephFS directory structures, goes from a \(40\times\) slowdown
for 10K files to a \(90\times\) slowdown for 100K files. It is a well-known
problem that directory data structures do not scale when creating files in the
same directory~\cite{ren:sc2014-indexfs} and any mechanism that uses these data
structures will experience similar slowdowns. Other mechanisms that write
events to a journal ({\it e.g.} the persists, ``Volatile Apply") experience a
much less drastic slowdown because the journal data structure does not need to
be scanned for every operation. Events are written to the end of the journal without
even checking the validity ({\it e.g.}, if the file already exists for a create),
which is another form of relaxed consistency because the file system assumes the
application has resolved conflicting updates in a different way.

% RPCs vs. apply: calls to metadata server vs. RADOS
\subsubsection{Overhead of RPCs} ``RPCs" is \(66\times\) slower than ``Volatile
Apply" because sending individual metadata updates over the network is costly.
While ``RPCs" sends a request for every file create, ``Nonvolatile Apply"
writes all the updates to the in-memory journal and applies them to the
in-memory data structures in the metadata server. While communicating the
decoupled namespace directly to the metadata server is faster, communicating
through the object store (``Nonvolatile Apply") is \(10\times\) slower.

% TODO: why is apply so slow.  
% apply: no CephFS changes, pulls/pushes same RADOS obj.
% v_apply vs. apply/persist: communicating through RADOS
\subsubsection{Overhead of ``Nonvolatile Apply"} The cost of ``Nonvolatile
apply" is much larger than all the other mechanisms.  That mechanism was not
implemented as part of CudeleFS -- it was a debugging and recovery tool packaged
with CephFS. It works by iterating over the updates in the journal and pulling
all objects that {\it may} be affected by the update.  This means that two
objects are repeatedly pulled, updated, and pushed: the object that houses the
experiment directory and the object that contains the root directory ({\it
i.e.} \texttt{/}).  The cost of communicating through the object store is shown
by comparing the runtime of ``Volatile apply" + ``Global persist" to
``Nonvolatile Apply". These two operations end up with the same final metadata
state but using ``Nonvolatile Apply" is clearly inferior.

% persist vs. save: one disk vs. many
\subsubsection{Parallelism of the Object Store} Comparing ``Local" and ``Global
persist" demonstrates the bandwidth advantages of storing the journal in a
distributed object store. For 100K file creates, the ``Global Persist"
performance is \(1.5\times\) faster because the object store is leveraging the
collective bandwidth of the disks in the cluster. This benefit comes from the
object store itself but should be acknowledged when making decisions for the
application; the size of the object store can help mitigate the overheads of
globally persisting metadata updates.

\subsubsection{Journal Size} Figure~\ref{fig:behavior-journal-size} shows the
amount of storage per journal update (\(y\) axis) for the range of file creates
we tested (\(x\) axis). The increase in file size is linear with the number of
metadata creates and suggests that updates for a million files would be
\(2.5\text{KB}*1\text{ million files} = 2.38\text{GB}\). Transfer times for
payloads of this size on an HPC network are reasonable.\\

\noindent\textbf{Takeaway}: the CudeleFS mechanisms have overheads and costs
that can differ {\it by orders of magnitude}. CudeleFS gives users the ability
to compose these mechanisms based on their application's correctness
requirements and performance goals.

\subsection{Weak vs. Strong Consistency}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-strong-v-weak.png}
\caption{
[\href{https://...}{source}]
The RPC per metadata update of ``Strong Consistency" has a large
overhead compared to the decoupled namespace strategy of ``Weak
Consistency".\label{fig:slowdown-strong-weak}}
\end{figure}

@@

% Final file system metadata states are equivalent No guarantees while
% transitioning mechanisms
We compare these semantics because the final metadata states are equivalent.
CudeleFS makes no guarantees during execution of the mechanisms or when
transitioning semantics -- the semantics are guaranteed {\it once the mechanism
completes}. So if servers fail during a mechanism, metadata or data may be
lost.

% DeltaFS vs. BatchFS vs. POSIX: decoupled is faster
% (5-7x) vs. (90-104x) slower
% Does not scale?
% Strong Consistency > 10X slower than Weak Consistency 
\subsubsection{Speedups of Decoupled Namespaces} Weak consistency uses the
decoupled namespace strategy and shows up to a \(20\times\) speedup over the
traditional namespaces that use RPCs. Compared to the baseline the slowdown is
\(5-7\times\) for Strong Consistency, which emulates BatchFS and
\(90-104\times\) for Weak Consistency, which emulates DeltaFS.

% POSIX (no stream) vs. POSIX: cost of durability < consistency
\subsubsection{Durability \(<<\) Consistency} The \(1.15\times\) overhead of
Strong Consistency compared to Strong Consistency, No Fault Tolerance for
100K files is negligible. It suggests that the overhead of consistency is much
larger than the overhead of durability. This conclusion should be stronger as
we scale the number of files because the cost of streaming the journal into the
object store is constant. We omit the same analysis for Weak Consistency
because the runtimes are so short that the normalized slowdowns are misleading.

% Weak Consistency benefit not due to metadata format
\subsubsection{Metadata Formats} Because the metadata formats are the same for
all schemes we argue that the performance gain for decoupled namespaces comes
from relaxing the consistency guarantees and not from the metadata formats.\\

\noindent\textbf{Takeaway}: CudeleFS shows the true benefit of eventual
consistency, where we see over a \(100\times\) slowdown for achieving strong
consistency, in the worst case.

@@

\subsection{Benefits of Isolated Subtree Policies}

@@

% setup: 2cs sep dirs, 2cs DN, 1c malicious write
Next we show how CudeleFS can be programmed to block interfering clients. We
use the same problematic workload from Figure~\ref{fig:overhead-b}, where
clients write to their own private directories and another client interferes with a stream of creates at
30 seconds.  We also have another client write to a decoupled namespace and
merge its updates at 90 seconds.  We equip each client directory with the
configuration:

@@

\subsection{Scaling Serialized Merges}

CudeleFS serializes merge requests at the metadata server before applying the
updates to the in-memory metadata store. Merging concurrently is an
optimization for future work, but merges for the largest journal size we tested
were quite fast.  Furthermore, since we place no restrictions on the validity
of metadata inserted into the journal, we can avoid touching poorly scaling
data structures. In other words, we can scale linearly if we weaken our
consistency by never checking for the existence of files before creating files.

>>>>

We evaluate Cudele on a 15 node cluster, partitioned into 8 object storage
servers, 3 metadata servers, and 2 monitor servers. The object storage servers
double as clients which is fine because clients are CPU and memory bound while
object storage servers are disk IO bound. All daemons run as a single process
which is the default setting for Ceph and the nodes have 2 dual core 2GHz
processors with 8GB of RAM. There are three daemons per object storage server
(one for each disk formatted with XFS) and they share an SSD for the journal.
The nodes are running Ubuntu 12.04.4, kernel version 3.2.0-63 but all
experiments run in Docker containers; this makes it easier to tear down and
re-initialize the cluster ({\it e.g.}, dropping the kernel cache) between
experiments. For these experiments, we compare CephFS to our programmable
consistency and durability modifications, which we call Cudele.

@@

\subsection{Microbenchmarks}
\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-mechanisms.png}
\caption{
[\href{https://...}{source}]
The performance of the Cudele mechanisms normalized to the runtime of the
``Append Client Journal" mechanism (the runtime of writing \(n\) file creates
to the client's in-memory journal).  \label{fig:slowdown-mechanisms}}
\end{figure}

@@

Figure~\ref{fig:slowdown-mechanisms} shows the runtime of the Cudele
mechanisms for a single client creating files in the same directory, normalized
to the time it takes to write \(n\) file create updates to the client's
in-memory journal ({\it i.e.} the ``Append Client Journal" mechanism). Bars
above \(10^0\) are slower than the ``Append Client Journal" mechanism.
``Stream" is an approximation of the overhead and is calculated by subtracting
the runtime of the job with the journal turned off from the runtime with the
journal turned on.  The largest workload we tested is 100K file creates in the
same directory.  This is the maximum recommended size of a directory in CephFS;
preliminary experiments with larger directory sizes show memory problems.

{\it Poorly Scaling Data Structures:} Despite doing the same amount of
work, mechanisms that rely on poorly scaling data structures have large
slowdowns for the larger number of creates. For example, ``RPCs" which relies
on the internal CephFS directory structures, goes from a \(40\times\) slowdown
for 10K files to a \(90\times\) slowdown for 100K files. It is a well-known
problem that directory data structures do not scale when creating files in the
same directory~\cite{ren:sc2014-indexfs} and any mechanism that uses these data
structures will experience similar slowdowns. Other mechanisms that write
events to a journal ({\it e.g.} the persists, ``Volatile Apply") experience a
much less drastic slowdown because the journal data structure does not need to
be scanned for every operation. Events are written to the end of the journal without
even checking the validity ({\it e.g.}, if the file already exists for a create),
which is another form of relaxed consistency because the file system assumes the
application has resolved conflicting updates in a different way.

% RPCs vs. apply: calls to metadata server vs. RADOS
{\it Overhead of RPCs:} ``RPCs" is \(66\times\) slower than ``Volatile
Apply" because sending individual metadata updates over the network is costly.
While ``RPCs" sends a request for every file create, ``Nonvolatile Apply"
writes all the updates to the in-memory journal and applies them to the
in-memory data structures in the metadata server. While communicating the
decoupled namespace directly to the metadata server is faster, communicating
through the object store (``Nonvolatile Apply") is \(10\times\) slower.

% TODO: why is apply so slow.  
% apply: no CephFS changes, pulls/pushes same RADOS obj.
% v_apply vs. apply/persist: communicating through RADOS
{\it Overhead of ``Nonvolatile Apply":} The cost of ``Nonvolatile
apply" is much larger than all the other mechanisms.  That mechanism was not
implemented as part of Cudele -- it was a debugging and recovery tool packaged
with CephFS. It works by iterating over the updates in the journal and pulling
all objects that {\it may} be affected by the update.  This means that two
objects are repeatedly pulled, updated, and pushed: the object that houses the
experiment directory and the object that contains the root directory ({\it
i.e.} \texttt{/}).  The cost of communicating through the object store is shown
by comparing the runtime of ``Volatile apply" + ``Global persist" to
``Nonvolatile Apply". These two operations end up with the same final metadata
state but using ``Nonvolatile Apply" is clearly inferior.

% persist vs. save: one disk vs. many
{\it Parallelism of the Object Store:} Comparing ``Local" and ``Global
persist" demonstrates the bandwidth advantages of storing the journal in a
distributed object store. For 100K file creates, the ``Global Persist"
performance is \(1.5\times\) faster because the object store is leveraging the
collective bandwidth of the disks in the cluster. This benefit comes from the
object store itself but should be acknowledged when making decisions for the
application; the size of the object store can help mitigate the overheads of
globally persisting metadata updates.

{\it Journal Size:} Figure~\ref{fig:behavior-journal-size} shows the
amount of storage per journal update (\(y\) axis) for the range of file creates
we tested (\(x\) axis). The increase in file size is linear with the number of
metadata creates and suggests that updates for a million files would be
\(2.5\text{KB}*1\text{ million files} = 2.38\text{GB}\). Transfer times for
payloads of this size on an HPC network are reasonable.\\

\noindent\textbf{Takeaway}: the Cudele mechanisms have overheads and costs
that can differ {\it by orders of magnitude}. Cudele gives users the ability
to compose these mechanisms based on their application's correctness
requirements and performance goals.

\subsection{Use Case 1: Creates in the Same Directory}
\label{use-case-1}

Clients creating files in private directories is heavily
studied in HPC~\cite{plfs, cephfs04, indexfs, giga+, batchfs, deltafs,
sevilla:eurosys, shardfs, mantle}, mostly due to checkpoint-restart~\cite{}.
But the workload also appears in cloud workloads, where systems like Hadoop use
the file abstraction to exchange work units to workers or to indicate when jobs
complete~\cite{}. A more familiar example is uncompressing an archive ({\it
e.g.}, \texttt{tar xzf}), where the file system services a flash crowd of
creates across all directories as shown in Figure~\ref{fig:overhead-creates}.
We use this as a microbenchmark because it allows us to control the size of the
log, since each create creates a single journal event.

\begin{figure}[tb]
\centering
\includegraphics[width=1.0\linewidth]{graphs/slowdown-strong-v-weak.png}
\caption{
[\href{https://...}{source}]
The RPC per metadata update of ``Strong Consistency" has a large
overhead compared to the decoupled namespace strategy of ``Weak
Consistency".\label{fig:slowdown-strong-weak}}
\end{figure}

@@

% Final file system metadata states are equivalent No guarantees while
% transitioning mechanisms
We compare these semantics because the final metadata states are equivalent.
Cudele makes no guarantees during execution of the mechanisms or when
transitioning semantics -- the semantics are guaranteed {\it once the mechanism
completes}. So if servers fail during a mechanism, metadata or data may be
lost.\\

% DeltaFS vs. BatchFS vs. POSIX: decoupled is faster
% (5-7x) vs. (90-104x) slower
% Does not scale?
% Strong Consistency > 10X slower than Weak Consistency 
{\it Speedups of Decoupled Namespaces:} Weak consistency uses the
decoupled namespace strategy and shows up to a \(20\times\) speedup over the
traditional namespaces that use RPCs. Compared to the baseline the slowdown is
\(5-7\times\) for Strong Consistency, which emulates BatchFS and
\(90-104\times\) for Weak Consistency, which emulates DeltaFS.\\

% POSIX (no stream) vs. POSIX: cost of durability < consistency
{\it Durability \(<<\) Consistency:} The \(1.15\times\) overhead of
Strong Consistency compared to Strong Consistency, No Fault Tolerance for
100K files is negligible. It suggests that the overhead of consistency is much
larger than the overhead of durability. This conclusion should be stronger as
we scale the number of files because the cost of streaming the journal into the
object store is constant. We omit the same analysis for Weak Consistency
because the runtimes are so short that the normalized slowdowns are misleading.\\

% Weak Consistency benefit not due to metadata format
{\it Metadata Formats:} Because the metadata formats are the same for
all schemes we argue that the performance gain for decoupled namespaces comes
from relaxing the consistency guarantees and not from the metadata formats.\\

\noindent\textbf{Takeaway}: Cudele shows the true benefit of eventual
consistency, where we see over a \(100\times\) slowdown for achieving strong
consistency, in the worst case.

\subsubsection{Network Bandwidth}
% 1G - 10G
\subsubsection{Number of Clients}
% up to 30 clients
\subsubsection{Number of Serialized Merges}

Cudele serializes merge requests at the metadata server before applying the
updates to the in-memory metadata store. Merging concurrently is an
optimization for future work, but merges for the largest journal size we tested
were quite fast.  Furthermore, since we place no restrictions on the validity
of metadata inserted into the journal, we can avoid touching poorly scaling
data structures. In other words, we can scale linearly if we weaken our
consistency by never checking for the existence of files before creating files.

@@

\subsection{Use Case 2: Creates with Rogue Client}
Clients create files in private directories and a separate client, which we
call a ``rogue" client, creates files in each directory. This introduces false
sharing and the metadata server revokes capabilities on directories touched by
the rogue client. While HPC tries to avoid these situations with
worklflows~\cite{batchfs, deltafs}, it stills happens in distributed file
systems when users unintentionally access directories in a shared file system.

@@

% setup: 2cs sep dirs, 2cs DN, 1c malicious write
Next we show how Cudele can be programmed to block interfering clients. We
use the same problematic workload from Figure~\ref{fig:overhead-b}, where
clients write to their own private directories and another client interferes with a stream of creates at
30 seconds.  We also have another client write to a decoupled namespace and
merge its updates at 90 seconds.  We equip each client directory with the
configuration:

@@

\subsection{Use Case 3: Read while Writing}

### 2017-10-17 paper/sections/7_conclusion.tex
paper: re-org eval and intro
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

%\section{Discussion}
%
%% Could we have implemented this on something other than CephFS?
%One question that comes up often in our work with Ceph is: ``Why do we always
%choose Ceph and can we implement this on another storage system?" Ceph is
%popular, robust, and open source -- getting it merged into mainline has a
%better chance of getting used than if we had built the system `clean-slate'
%from the ground up. Using Ceph, we can also leverage its robustness using an
%approach called ``programmability".
%
%% How awesome programmability is
%``Programmability" is a way of designing storage systems that encourages code
%re-use and composition.  A programmable storage system exposes internal
%subsystem as building blocks for higher level services. This `dirty-slate'
%approach limits redundant code and leverages the robustness of the underlying
%storage system. CudeleFS uses this approach and re-uses some of the building
%blocks from the Malacology programmable storage system~\cite{sevilla:eurosys17}
%to great success and requires only:
%
%\begin{itemize}
%
%  \item 354 lines of library code
%
%  \item 219 lines of non-destructive metadata server code, which is not used
%  unless it is turned on
%
%  \item 4 lines of destructive client/server code to check whether a namespace
%  is decoupled
%
%\end{itemize}

@@

Relaxing consistency and durability semantics in the file system is a
double-edged sword. While it achieves better performance and scalability, it
alienates applications that rely on strong consistency and durability. CudeleFS
lets users assign consistency and durability guarantees to subtrees in
the global namespace, giving users a wide range of policies and
optimizations that can be custom fit to the application. Using CudeleFS, we
compare related work on the same file system and conclude that strong
consistency can cause a 104\(\times\) slow down while merging updates and
maintaining durability only have between a \(7-10\times\) slow down.

>>>>

%\section{Discussion}
%
%% Could we have implemented this on something other than CephFS?
%One question that comes up often in our work with Ceph is: ``Why do we always
%choose Ceph and can we implement this on another storage system?" Ceph is
%popular, robust, and open source -- getting it merged into mainline has a
%better chance of getting used than if we had built the system `clean-slate'
%from the ground up. Using Ceph, we can also leverage its robustness using an
%approach called ``programmability".
%
%% How awesome programmability is
%``Programmability" is a way of designing storage systems that encourages code
%re-use and composition.  A programmable storage system exposes internal
%subsystem as building blocks for higher level services. This `dirty-slate'
%approach limits redundant code and leverages the robustness of the underlying
%storage system. Cudele uses this approach and re-uses some of the building
%blocks from the Malacology programmable storage system~\cite{sevilla:eurosys17}
%to great success and requires only:
%
%\begin{itemize}
%
%  \item 354 lines of library code
%
%  \item 219 lines of non-destructive metadata server code, which is not used
%  unless it is turned on
%
%  \item 4 lines of destructive client/server code to check whether a namespace
%  is decoupled
%
%\end{itemize}

@@

Relaxing consistency and durability semantics in the file system is a
double-edged sword. While it achieves better performance and scalability, it
alienates applications that rely on strong consistency and durability. Cudele
lets users assign consistency and durability guarantees to subtrees in
the global namespace, giving users a wide range of policies and
optimizations that can be custom fit to the application. Using Cudele, we
compare related work on the same file system and conclude that strong
consistency can cause a 104\(\times\) slow down while merging updates and
maintaining durability only have between a \(7-10\times\) slow down.
